Yelp Academic Dataset Final Report

### 2016-08-09 paper/paper.Rmd
data changed little

Lastly, business data, user data and review data were all used to analyze the users’ behaviors when they are in unfamiliar locations User data was cleaned to filter for active users with a significant amount of reviews. Cleaned review data and business data were then joined together with user data. We created an additional boolean column called ‘most_revieSwed’, after computing a user's "home" (state where they reviewed the most). Using this, we cleaned up and created a new data frame with average star ratings of familiar places and unfamiliar places per user. In the next section, we discuss this further along with results. 
```{r load_users, echo = FALSE}
users <- read_csv("../clean_data/yelp_users.csv")
reviews <- read_csv("../clean_data/yelp_reviews.csv")
```
####Stage Three: Pre-Processing using ‘tidytext’ for Sentiment Analysis
Sentiment analysis, or opinion mining, makes use of natural language processing to analyze pieces of text and determine the attitude of the speaker or writer. To perform sentiment analysis, we researched various text mining libraries. First, "__tm__" was used to remove stop words, common English words that would give no information, but the process of splitting text reviews into one word-per-row and removing stop words was too inefficient. After more research, we came across “__tidytext__”, a library for text mining. Using this library, cleaning and aggregating the review data was extremely easy and efficient. We then performed tidy analysis to strip reviews and tokenize each word into a single row in the data-frame.

>>>>

Lastly, business data, user data and review data were all used to analyze the users’ behaviors when they are in unfamiliar locations User data was cleaned to filter for active users with a significant amount of reviews. Cleaned review data and business data were then joined together with user data. We created an additional boolean column called ‘most_revieSwed’, after computing a user's "home" (state where they reviewed the most). Using this, we cleaned up and created a new data frame with average star ratings of familiar places and unfamiliar places per user. In the next section, we discuss this further along with results. 
```{r load_users, echo = FALSE}
users <- read_csv("../clean_data/yelp_users.csv")
```
####Stage Three: Pre-Processing using ‘tidytext’ for Sentiment Analysis
Sentiment analysis, or opinion mining, makes use of natural language processing to analyze pieces of text and determine the attitude of the speaker or writer. To perform sentiment analysis, we researched various text mining libraries. First, "__tm__" was used to remove stop words, common English words that would give no information, but the process of splitting text reviews into one word-per-row and removing stop words was too inefficient. After more research, we came across “__tidytext__”, a library for text mining. Using this library, cleaning and aggregating the review data was extremely easy and efficient. We then performed tidy analysis to strip reviews and tokenize each word into a single row in the data-frame.
